Predicting Diabetes Based on Various Factors Using logistic Regression

### 2023-11-13 manuscript/manuscript.tex
Formatting issues
Continuation of methods including the creation of table 2

\section{Results}
\label{sec:resu}

>>>>

    After exploring the descriptive statistics, I will begin to perform a logistic regression. Logistic regression, is used to describe the data and the relationship between one dependent variable against many independent variables. In this particular case, we will be looking at the binary response of diabetes with the various independent variables including but not limited to; pregnancies and glucose levels. To begin, I will split the data into a training and a test set. This will be done by setting a random seed of 30 and using 80 percent of the data set in the training set and the remaining 20 percent as the testing set. We will next begin to build the logistic regression model using the training data.

    In Table~\ref{tab:sl} you will see the output of each predictor on predicting the outcome of diabetes. This table will provide us with coefficients, the standard errors, the z-scores, and finally the p-value for each predictor in the model. Based on the output, we can determine that only skin thickness is not statistically significant in predicting if a patient may have diabetes. Therefore, all of the other predictors are statistically significant and should be monitored in predicting diabetes.

\begin{table}[ht]
    \caption{Summary of Logistic Regression Model}
    \label{tab:sl}
\centering
\begin{tabular}{lrrrr}
  \hline
Predictor & Estimate & Std. Error & z value & Pr($>$$|$z$|$) \\ 
  \hline
(Intercept) & -8.02 & 0.41 & -19.73 & 0.00 \\ 
  Pregnancies & 0.11 & 0.02 & 6.04 & 0.00 \\ 
  Glucose & 0.03 & 0.00 & 16.34 & 0.00 \\ 
  BloodPressure & -0.01 & 0.00 & -3.69 & 0.00 \\ 
  SkinThickness & 0.00 & 0.00 & 0.26 & 0.79 \\ 
  Insulin & -0.00 & 0.00 & -2.74 & 0.01 \\ 
  BMI & 0.08 & 0.01 & 9.07 & 0.00 \\ 
  DiabetesPedigreeFunction & 0.76 & 0.17 & 4.38 & 0.00 \\ 
  Age & 0.02 & 0.01 & 3.03 & 0.00 \\ 
   \hline
\end{tabular}
\end{table}
\section{Results}
\label{sec:resu}
